An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-11-01 scagnostics.Rmd
more on data description

- **pipe**: nuisance directions are generated by sampling independently from a uniform distribution between $[-1,1]$, and the circle is generated by sampling randomly on a 2D circle, and adding a small radial noise.
- **sine**:  nuisance directions are generated by sampling independently from a standard normal distribution, and the sine curve is generated by $x_n = \sin(x_{n-1}) + \mathrm{jittering}$.
- **spiral**:  nuisance directions are generated by sampling independently from a normal distribution, and the structure directions are sampled from an Archimedean spiral, i.e. $r = a + b \theta$, with $a=b=0.1$ and we sample angles $\theta$ from a normal distribution with mean 0 and variance $2\pi$, giving a spiral with higher densities at lower radii. The absolute value of $\theta$ fixes the direction of the spiral shape.

Two samples sizes are also used: $n=100$ (small) and $n=1000$ (large).

>>>>

- **pipe**: nuisance directions are generated by sampling independently from a uniform distribution between $[-1,1]$, and the circle is generated by sampling randomly on a 2D circle, and adding a small radial noise. The circle should be easy to see by some indices because it is large structure, but the nonlinearity creates a complication. 
- **sine**:  nuisance directions are generated by sampling independently from a standard normal distribution, and the sine curve is generated by $x_n = \sin(x_{n-1}) + \mathrm{jittering}$. The sine is medium nonlinear structure, which should be visible by multiple indices.
- **spiral**:  nuisance directions are generated by sampling independently from a normal distribution, and the structure directions are sampled from an Archimedean spiral, i.e. $r = a + b \theta$, with $a=b=0.1$ and we sample angles $\theta$ from a normal distribution with mean 0 and variance $2\pi$, giving a spiral with higher densities at lower radii. The absolute value of $\theta$ fixes the direction of the spiral shape. This is fine structure which is only visible close to the optimal projection.

Two samples sizes are also used: $n=(100, 1000)$.
